---
title: "Learn R Part I Exercises"
format: html
editor: visual
---

Welcome to your first Quarto document! This is where you will try out all of the hands-on exercises in the workshop, starting with step 04.

```{r}
# load packages here (ignore this until step 07)

```

## 04. How do I write and run code in a coding notebook?

#### **Your Turn!**

Write and run code that finds the square root of 60

Hint: the square root function in R is `sqrt()`

```{r}

```

## 05. What is an object and how do I create one?

#### **Your Turn!**

Create an object called `my_age` that stores your age, then call the object so it prints to the Console.

```{r}

```

## 06. What are vectors in R?

#### **Your Turn!**

1.  Create a vector containing 5 numbers

2.  Add 4 to each number

3.  Use an R function to return the minimum value in your vector

```{r}

```

## 07. **What are R packages and how do I load them?**

#### **Your Turn!**

1.  Install {tidyverse} directly in the console by typing `install.packages("tidyverse")` next to the `>` and pressing `Enter`.

2.  At the beginning of your Quarto document, load {tidyverse} by typing `library("tidyverse")` in the designated code chunk and running the code chunk.

## 08. **How do I import data?**

#### **Your Turn!**

Load the colleges data using `read_csv()`. You can name your data frame object `se_colleges`

```{r}

```

## 09. **How can I get familiar with my data?**

#### **Your Turn!**

Use one or more of the methods in this section to determine the following about `se_colleges`:

1.  How many 4-year colleges are in the U.S. southeast? (Hint: there is one row per college)

2.  What type of variable is `institution_name`? What about `n_admitted`?

```{r}

```

## 10. **What are some ways I can transform my data?**

### 10.1 Subset rows with `filter()`

#### **Your Turn!**

Filter the rows in `se_colleges` to only include HBCUs (Historically Black Colleges and Universities) in VA and NC that enrolled fewer than 500 students.

*Notes:* `hbcu` is a binary variable (1 or 0), where 1 indicates a college is an HBCU.

```{r}

```

### 10.2 Subset columns with `select()`

#### **Your Turn!**

Subset the columns in `se_colleges` to only include `institution_name` and the three variables that start with "`n_`".

```{r}

```

### 10.3 Sort rows with `arrange()`

#### **Your Turn!**

What are the top 3 HBCUs by number of applicants?

*Note:* `hbcu` is a binary variable (1 or 0), where 1 indicates a college is an HBCU.

```{r}

```

### 10.4 Create new variables with `mutate()`

#### **Your Turn!**

Add two new variables to `se_colleges` (you come up with their names):

1.  Acceptance rate (admitted divided by applied)
2.  Yield rate (enrolled divided by admitted)

Then, add a pipe and filter only to colleges with an acceptance rate below .15 and a yield rate above .5. Which colleges meet these criteria?

```{r}

```
