---
title: "Learn R Part I In-class Solutions"
format: html
editor: visual
---

```{r}
# load tidyverse
library(tidyverse)
```

## 05. How do I write and run code in a coding notebook?

Write and run code that finds the square root of 60

Hint: the square root function in R is `sqrt()`

```{r}
# find sq root
sqrt(60)
```

## 06. What is an object and how do I create one?

Create an object called `my_age` that stores your age, then call the object so it prints to the Console.

```{r}
# store object
my_age <- 32

# call object
my_age
```

## 08. **How do I import data?**

Load the Taylor Swift data using `read_csv()`. You can name your data frame object `tswift`

```{r}
# load data
tswift <- read_csv("data/taylor_swift_spotify.csv")
```

## 09. **How can I get to know my variables?**

Using `summary()`, determine whether the mean or median of `danceability` is greater.

***Median is slightly greater (.59 vs. .58)***

```{r}
# check out danceability
summary(tswift$danceability)
```

## 10. **What are some ways I can transform my data?**

### 10.1 Subset rows with `filter()`

Filter `tswift` to only contain songs that are *NOT* on the "Lover" album

```{r}
# filter out Lover
tswift |> 
  filter(album != "Lover")
```

### 10.2 Subset columns with `select()`

Limit the columns in `tswift` to only include `name` and `speechiness`

```{r}
# subset columns
tswift |> 
  select(name, speechiness)
```

### 10.3 Sort rows with `arrange()`

Find the 3 most popular Taylor Swift songs (according to Spotify)

*Hint:* Browse the environment pane for the variable that measures this (it's near the bottom)

```{r}
# sort by popularity (descending)
tswift |> 
  arrange(desc(popularity)) |> 
  select(name, popularity)
```

### 10.4 Create new variables with `mutate()`

Create a new variable in `tswift` that multiplies `danceability` by 100 (you pick the name of the new variable), then limit your columns to `name`, `danceability`, and your new variable.

Note: The symbol for multiplication in R is `*`

```{r}
# new variable + subset columns
tswift |> 
  mutate(dance_100 = danceability * 100) |> 
  select(name, danceability, dance_100)
```
